\documentclass[12pt]{niuthesis}
% \documentclass[12pt,singlespacing]{niuthesis}

% some packages are loaded here
\usepackage{latexsym}		% to get LASY symbols
\usepackage{graphicx}		% to insert PostScript figures
\usepackage{rotating}           % defines sidways table and figure env.
\usepackage{amsmath}
% \usepackage{hyperref}		% to insert hyperrefs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some LaTeX macros

\newcommand{\twochoices}[2]{\left\{ \begin{array}{lcc}
        \displaystyle #1 \\ \vspace{-10pt} \\
        \displaystyle #2 \end{array} \right. } %}

\newcommand{\twovec}[2]{\left(\begin{array}{c} #1 \\ #2 \end{array}\right)}

\newcommand{\twomatrix}[4]{\left(\begin{array}{cc} #1 & #2 \\ 
     #3 & #4 \end{array}\right)}

% Uncomment the following line for a List of Symbols
% \newcommand{\listofXXX}{\input{symbols}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Choose the chapter(s) / files you want to work with

%%% use this to compile all chapters
\def\files{ch1,ch2,ch3,refs,app1,app2}

%%% use this to work with only one chapter
% \def\files{ch2}

\includeonly{\files}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\title{Magnetometer-less State-Estimation \\ of a Unicycle Model Mobile
Robot \\ using a Cascaded Kalman Filter Framework}

\author{Tommy Le}

\major{Mechanical Engineering}
\degree{Thesis}{M.S.}{Masters of Science}
\degreedate{Dec}{2023}
\department{Department of Mechanical Engineering}
\director{Dr. Ji-Chul Ryu}

\begin{abstract}
Localization is one of the most important aspects in the development of  
autonomous mobile robots. For effective navigation of these robots, 
an efficient localization algorithm is needed. Typical localization, or
state-estimation algorithms, require an IMU along with an external reference 
that provides highly-precise pose information, such as a GNSS for outdoor 
applications. In indoor applications, GNSS data is not accessible so many 
mobile robot implementations turn to magnetometers to provide the additional pose 
information. However, with the push to miniaturize these robotic systems, 
magnetometers are not always reliable due to their close proximity to motors and 
other electronics, causing magnetic distortion and in turn, incorrect pose 
information. To address this issue, this thesis proposes a magnetometer-less 
state-estimation algorithm based on a cascaded Extended Kalman Filter (EKF) framework 
for localization of an autonomous mobile robot. The presentation will include 
background information on estimation and the Kalman Filter, explanation of the
mathematical models for the algorithm, as well as simulation results, proving 
the feasibility for physical implementation on a mobile robot. 
\end{abstract}

\begin{acknowledgments}
  Here's where you acknowledge folks who helped.

\end{acknowledgments}

\begin{dedication}
  To all of the fluffy kitties.

\end{dedication}

% comment this to suppress prologue
\MakeThesisPrologue % includes table of contents
% \tableofcontents

\include{ch1}		% file with Chapter 1 contents
\include{ch2}		% file with Chapter 2 contents
\include{ch3}   % file with Chapter 3 contents
\include{refs}	% file with references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  Appendices

\appendix
\include{app1}			% file with Appendix A contents
\include{app2}			% file with Appendix B contents

\end{document}
